An increasing number of convenience stores as well as medium-scale and small-scale supermarkets appears in our surroundings. 
To make a long-term profit, retailers desire to keep their overall cost as low as possible in terms of management, labor, logistics and properties. 
News: home depot yearly labor cost 90,444 million.
costco yearly logistics cost 10,444 million.
warehouse, amazon, alibaba 
Walmart, home depot, caref, costco,

% thought of advanced su ma comes up much earlier. attaching rfid tag on
% items\cite{}, quick checkout , self checkout

amazon robot
https://www.youtube.com/watch?v=cLVCGEmkJs0

end-user
Meanwhile, a concept of "cashier-free supermarket" is proposed in nowadays, which draws much public attention. 
The number of unmanned supermarkets is increasing, and it is becoming an emerging business model in the future, for an instance,  the novel idea of ¡°Take it away¡±as announced by Amazon Go.
Amazon Go, Sam's Club Now and Taocafe are three pioneers that jump into the "cashier-free supermarket" technology and make it come true. 
Amazon Go already started 5 unmanned stores in U.S. and they are planning to open up to 1000 stores till 2020. 
Sensors and camera scan detect the categories and quantities of the products that a customer takes. %, and can make a preliminary settlement. 
Moreover, with a proper camera layout, more integrated information can be gathered to strengthen our estimation of the quantitative variation of the products\cite{ERDEM2006156}. 
Camera monitoring the purchasing behavior is an important part in a "cashier-free supermarket", and the change from a traditional supermarket to an advanced supermarket can be achieved by upgrading the capabilities and layouts of cameras, to provide an identification feature.
This paper will discuss the techniques of the modern cameras, mainly about device layouts, items category identification and quantity counting. [update todo]
%layout to cover all scene suitable

The rest of this paper is structured as follows:
Section \ref{sec:rw} xxxx
Section \ref{sec:rw} xxxx
 xxxx in Section \ref{sec:rw}.

