\section{Related Works}
\label{sec:rw}

Amazon Go and Sam's Club Now are two popular retailers in unmanned supermarket.
Amazon Go stores use a combination of sensors on the shelves, cameras and computer vision with machine learning.
Different from Amazon Go, Sam's Club  pays more attention to camera layout aiming to plan shopping routes, and it use RFID\cite{1192765}.
In our experiment, we learnt from both retailers, and we set camera layout first, then use computer vision and sensors to identity the category and quantity of the items.

\subsection{Camera layout}

In order to lower the overall cost of the sellers and economize resources, we aim to use the less cameras to cover whole scene while  the clearest image can be obtained.
We compare the camera layout of various supermarkets and chose one of the best-functioned layouts of cameras for our experiment, which use multi cameras and each camera is responsible for a specific area.
We can get all the information in this area，and image obtained for each region are processed separately\cite{}.
We try to adjust the Field of View (FOV) aiming to ensure both, camera coverage maximizing and image clarity\cite{ERDEM2006156}.

\subsection{Computer vision}
Two popular computer visions are YOLO and Faster-RCNN\cite{NIPS2015_5638}\cite{yolov3}.
Both of them have strong recognition ability. Faster-RCNN is a technology for using CNN to research feature map, and RPN network will complete the full operation of the map before send it to box regression layer and taxonomy\cite{NIPS2015_5638}.
YOLO input S×S grid, and every gird is responsible for the objects falling into it, then it can choose the maximal IOU of bounding box\cite{yolov3}.
YOLOv3 is chosen in our experiment since in processing medium-scale and small-scale supermarkets, it is based on Open Source Computer Vision Library(OpenCV) and Compute Unified Device Architecture(CUDA).
OpenCv is used to images processing, and CUDA is used to call GPU to accelerated operation.

\subsection{Weight sensor}
Amazon Go use the weight sensors as an assistant to determine the number of items on the shelves.

\section{ Technical comparison }

\subsection{official tones}

Amazon Go officials stressed that they could use computer vision, sensor fusion, and deep learning to make people’s shopping more convenient.
The store concept is considered as a revolutionary model which relies on the prevalence of smartphones and geofencing technology to streamline the customer experience, as well as supply chain and inventory management\cite{GREWAL20171} .


\subsection{end-user comments}

According to some end-user comments, the existence of trans-era science and technology changes our consumption pattern. However, some people think it  makes shopping a hassle since Amazon Go omitted the need for closing account by human, and it is hard for the aged to use smartphone.

ESL: electronic shelf label
small fontsize for elderly people

60yrs age grandma.
samsclub , membership fee.  self check-out on smartphones.  reduce cost, incurring burden onto customers.

younger adults, students
no line, quick, smartphone 

proofread
